Formalizing Stack Safety as a Security Property

### 2021-07-09 submission3/main.tex
Actually fixed merge

We improve upon \citet{SkorstengaardSTKJFP} in two significant ways:
\begin{enumerate}[label=(\roman*)]
\item Our definition captures the intuition that {\em
  every} caller should be protected from its callees.  By contrast,
\citet{SkorstengaardSTKJFP}
statically divide the world into trusted functions, which feature additional
dynamic ``reasonableness'' constraints on their behavior and for which their
properties hold, and adversary functions, which may violate those
constraints but are not guaranteed safety. This static division
is insufficient when we consider buggy, but not inherently adversarial,
code --- one can imagine a function that, when called with the wrong
inputs, behaves unreasonably, but under most circumstances can be
considered reasonable. \citet{SkorstengaardSTKJFP} would be forced
to classify such a function as an adversary, and would not guarantee it
protection.
\apt{But see p. 17 para 2 of the JFP version of their paper, where they explicitly
  dispute this characterization!}
\sna{But on p. 30, Definition 5, the JFP version still clearly defines that to be reasonable,
  a component must {\em always} behave reasonably. And immediately after states that the
  adversarial code can {\em never} be given LSE and WBCF guarantees. I suppose I'll cite that
  definition directly.}
We argue that if individual function activations are well-behaved,
they should be protected.

>>>>

We improve upon \citet{SkorstengaardSTKJFP} in two significant ways:
\begin{enumerate}[label=(\roman*)]
\item Our definition captures the intuition that {\em
  every} caller should be protected from its callees.  By contrast,
\citet{SkorstengaardSTKJFP}
statically divide the world into trusted functions, which feature additional
dynamic ``reasonableness'' constraints on their behavior and for which their
properties hold, and adversary functions, which may violate those
constraints but are not guaranteed safety. This static division
is insufficient when we consider buggy, but not inherently adversarial,
code --- one can imagine a function that, when called with the wrong
inputs, behaves unreasonably, but under most circumstances can be
considered reasonable. \citet{SkorstengaardSTKJFP} would be forced
to classify such a function as an adversary, and would not guarantee its
protection.
\apt{But see p. 17 para 2 of the JFP version of their paper, where they explicitly
  dispute this characterization!}
\sna{But on p. 30, Definition 5, the JFP version still clearly defines that to be reasonable,
  a component must {\em always} behave reasonably. And immediately after states that the
  adversarial code can {\em never} be given LSE and WBCF guarantees. I suppose I'll cite that
  definition directly.}
We argue that if individual function activations are well-behaved,
they should be protected.
In contrast in our setting, individual function well-behaved activations are protected.
